---
output:
  bookdown::pdf_document2:
    toc: FALSE
    number_sections: TRUE
    keep_tex: true
geometry: "left = 2.5cm, right = 2cm, top = 2cm, bottom = 2cm"
fontsize: 11pt
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \pagenumbering{gobble}
  - \usepackage{sectsty}
  - \usepackage{setspace}\spacing{1.5}
  - \usepackage{bm}
  - \DeclareUnicodeCharacter{0008}{ }
  - \setlength{\parindent}{4em}
  - \usepackage[hang,flushmargin,multiple]{footmisc}

linkcolor: blue
bibliography: bibliography.bib
csl: apa.csl
params:
  run_name: ["v2.0"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,
                      tidy = T,
                      message = F)

# load required R packages
library(here)         # For auto-locating files within the working directory
library(bookdown)     # For numbering figures, tables, and equations
library(stringr)      # For manipulating strings in figure captions
library(cowplot)      # For creating gridded plots
library(gridGraphics) # For including base R plots in gridded plots
library(formatR)      # For displaying tidy code in output
library(knitr)        # For making tidy tables
library(kableExtra)   # For formatting tables
library(tidyverse)    # For tidy data management
library(corrplot)     # For correlation plots

options(scipen=999) # turns off the use of scientific notation

# Save the directory from which to pull results files
run_dir <- here::here("results", params$run_name)

# Load figures, tables, and values to include
load(file = file.path(run_dir, "plots.RData"))
load(file = file.path(run_dir, "tables.RData"))
load(file = file.path(run_dir, "values.RData"))
```

\pagenumbering{gobble}

\begin{center}

LANDSCAPE INFLUENCES ON THERMAL SENSITIVITY AND PREDICTED SPATIAL VARIABILITY AMONG BROOK TROUT STREAMS IN THE SOUTHEASTERN USA

George P. Valentine\footnote{Dept. of Fish, Wildlife, \& Conservation Biology, Colorado State University, Fort Collins, Colorado 80523 USA}\footnote{Graduate Degree Program in Ecology, Colorado State University, Fort Collins, Colorado 80523 USA},
Xinyi Lu\footnotemark[1],
C. Andrew Dolloff\footnote{U.S. Forest Service Southern Research Station, Dept. of Fisheries and Wildlife, Virginia Polytechnic Institute and State University, Blacksburg, Virginia, 24061, USA},
Craig N. Roghair\footnotemark[3],
Jacob M. Rash\footnote{Inland Fisheries Division, North Carolina Wildlife Resources Commission, 645 Fish Hatchery Road, Marion, NC, 28752, USA},
Mevin B. Hooten\footnote{Dept. of Statistics \& Data Sciences, The University of Texas at Austin, Austin, Texas 78712 USA},
Yoichiro Kanno\footnotemark[1]\footnotemark[2]
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\footnote[1]{Corresponding Author: yoichiro.kanno@colostate.edu}


\today

\end{center}

\vfill

\newpage

# Acknowledgements {-}
This research was funded by Cooperative Agreement No. G21AC10205 from the U.S. Geological Survey Southeast Climate Adaptation Science Center, and Cooperative Agreement F20AC11372 from the U.S. Fish and Wildlife Service. The findings and conclusions in this paper are those of the authors and do not necessarily represent the views of the U.S. Geological Survey and U.S. Fish and Wildlife Service. The authors certify that they have no conflicting interests, financial or otherwise, that might be perceived as influencing their objectivity.

\newpage

```{r abstract, child = 'abstract.Rmd'}
```

\newpage
\pagenumbering{arabic}

# Introduction

```{r intro, child = 'introduction.Rmd'}
```

# Methods

```{r methods, child = 'methods.Rmd'}
```

# Results

```{r results, child = 'results.Rmd'}
```

# Discussion

```{r discussion, child = 'discussion.Rmd'}
```

\newpage

# References {-}

```{r biblio, child = 'bibliography.Rmd'}
```

\newpage

# Appendix

```{r appendix, child = 'appendix.Rmd'}
```
