---
title: ''
output: bookdown::pdf_document2
---
## Principal Components Analysis
The first principal component was dominated by estimates of monthly and annual stream flow (Table \@ref(tab:PCs-table)). The second principal component was made up of metrics of spring and summer stream velocity. The third principal component included winter stream velocity and elevation, but also incorporated estimated temperature maximums within the catchment. The fourth principal component included groundwater (baseflow and water table depth), precipitation estimates, and minimum temperatures. The fifth and final principal component was dominated by measures of soil moisture, urban and deciduous landcover, and local colluviated (unconsolidated) sediment. The first five principal components explained `r round(pca_summary.table["Cumulative R2", "PC5"], 3) * 100`% of the variance in predictors (Table \@ref(tab:PCs-table)).

(ref:PCs-table-cap) Top five principal components (PCs) by variance explained (R$^2$). The top ten contributing variables for each principal component are included. "Q" variables refer to stream flow metrics during specified periods of the year (numbers = months and MA = mean annual), and "V" variables refer to stream velocity. Further variable definitions are available from the [NHDPlus User Guide](https://pubs.er.usgs.gov/publication/ofr20191096) and [EPA StreamCat](https://www.epa.gov/national-aquatic-resource-surveys/streamcat-metrics-and-definitions) database.

```{r PCs-table}
kbl(top.loadings.table,
    caption = "(ref:PCs-table-cap)") %>% 
  #column_spec(6, width = "3cm") %>% 
  kable_styling(full_width = T,
                latex_options = "HOLD_position") %>% 
  kable_classic()
```

## Hierarchical Models
### Model Comparison
All parameters converged at $\hat{r}$ values of 1.1 or less. Models of weekly maximum temperature offered a superior fit to daily maximum temperature, and the nonlinear models outperformed the linear models. For the linear models, DIC improved from `r Daily_LM_DIC.val` to `r Weekly_LM_DIC.val` and RMSE improved from `r round(model_RMSEs.table[1,2], 2)` (95% HPDI: `r round(model_RMSEs.table[1,4], 2)` to `r round(model_RMSEs.table[1,5], 2)`) to `r round(model_RMSEs.table[2,2], 2)` (95% HPDI: `r round(model_RMSEs.table[2,4], 2)` to `r round(model_RMSEs.table[2,5], 2)`) going from the daily to weekly time scale. For the nonlinear models, DIC improved from `r Daily_Logistic_DIC.val` to `r Weekly_Logistic_DIC.val` and RMSE improved from `r round(model_RMSEs.table[3,2], 2)` (95% HPDI: `r round(model_RMSEs.table[3,4], 2)` to `r round(model_RMSEs.table[3,5], 2)`) to `r round(model_RMSEs.table[4,2], 2)` (95% HPDI: `r round(model_RMSEs.table[4,4], 2)` to `r round(model_RMSEs.table[4,5], 2)`) going from daily to weekly time scales. Posterior predictive checks were similar for linear and nonlinear models, suggesting little evidence of lack of fit between model estimates and data. Mean Bayesian p-values for mean and standard deviation for the linear model at the weekly time scale were `r round(Weekly_Max_LM_PPC_summ.table["Mean", 1], 2)` and `r round(Weekly_Max_LM_PPC_summ.table["Mean", 2], 2)`. Mean Bayesian p-values for the nonlinear model at the weekly scale were `r round(Weekly_Max_Logistic_PPC_summ.table["Mean", 1], 2)` and `r round(Weekly_Max_Logistic_PPC_summ.table["Mean", 2], 2)`.

### Thermal Sensitivity
Linear regression slopes were higher with temperatures summarized at the weekly time scale than the daily time scale (mean slope of `r round(mean(weekly_linear_slopes.table$mean), 2)` as compared to `r round(mean(daily_linear_slopes.table$mean), 2)`. Slopes ranged from `r round(min(daily_linear_slopes.table$mean), 2)` (95% HPDI = `r round(daily_linear_slopes.table[which.min(daily_linear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(daily_linear_slopes.table[which.min(daily_linear_slopes.table$mean), "95%_HPDU"], 2)`) to `r round(max(daily_linear_slopes.table$mean), 2)` (95% HPDI = `r round(daily_linear_slopes.table[which.max(daily_linear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(daily_linear_slopes.table[which.max(daily_linear_slopes.table$mean), "95%_HPDU"], 2)`) for temperatures at the daily time scale and from `r round(min(weekly_linear_slopes.table$mean), 2)` (95% HPDI = `r round(weekly_linear_slopes.table[which.min(weekly_linear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(weekly_linear_slopes.table[which.min(weekly_linear_slopes.table$mean), "95%_HPDU"], 2)`) to `r round(max(weekly_linear_slopes.table$mean), 2)` (95% HPDI = `r round(weekly_linear_slopes.table[which.max(weekly_linear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(weekly_linear_slopes.table[which.max(weekly_linear_slopes.table$mean), "95%_HPDU"], 2)`) for temperatures at the weekly time scale. Likewise, nonlinear regression maximum slopes were higher with temperatures summarized at the weekly time scale than the daily time scale (mean slope of `r round(mean(weekly_nonlinear_slopes.table$mean), 2)` as compared to `r round(mean(daily_nonlinear_slopes.table$mean), 2)`. Slopes ranged from `r round(min(daily_nonlinear_slopes.table$mean), 2)` (95% HPDI = `r round(daily_nonlinear_slopes.table[which.min(daily_nonlinear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(daily_nonlinear_slopes.table[which.min(daily_nonlinear_slopes.table$mean), "95%_HPDU"], 2)`) to `r round(max(daily_nonlinear_slopes.table$mean), 2)` (95% HPDI = `r round(daily_nonlinear_slopes.table[which.max(daily_nonlinear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(daily_nonlinear_slopes.table[which.max(daily_nonlinear_slopes.table$mean), "95%_HPDU"], 2)`) for temperatures at the daily time scale and from `r round(min(weekly_nonlinear_slopes.table$mean), 2)` (95% HPDI = `r round(weekly_nonlinear_slopes.table[which.min(weekly_nonlinear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(weekly_nonlinear_slopes.table[which.min(weekly_nonlinear_slopes.table$mean), "95%_HPDU"], 2)`) to `r round(max(weekly_nonlinear_slopes.table$mean), 2)` (95% HPDI = `r round(weekly_nonlinear_slopes.table[which.max(weekly_nonlinear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(weekly_nonlinear_slopes.table[which.max(weekly_nonlinear_slopes.table$mean), "95%_HPDU"], 2)`) for temperatures at the weekly time scale. Nonlinear measures of maximum slope were highly correlated with linear slopes (daily = `r round(cor(daily_linear_slopes.table$mean, daily_nonlinear_slopes.table$mean, method = "pearson"), 2)`, weekly = `r round(cor(weekly_linear_slopes.table$mean, weekly_nonlinear_slopes.table$mean, method = "pearson"), 2)`; Pearson's). Slopes were heterogeneous in space (Fig. \@ref(fig:slopes-map)). There was considerable spatial structure in these slopes (Appendix \@ref(fig:logistic-weekly-betas-semivariogram-plot)).

```{r slopes-map, fig.cap="Air-water temperature slopes for each of 203 measurement sites. Slopes are $\beta$ values from the nonlear model of maximum weekly temperatures."}
betas_map.plot
```

Correlation analysis demonstrated that there was a moderate association between thermal sensitivity (as measured by the nonlinear regression using weekly temperatures) and local landscape. Thermal sensitivity was most closely correlated with segment slope, baseflow index (an estimate of groundwater influence), winter flow, and stream segment location and drainage area ()\@ref(tab:weekly-logistic-betas-corr-table). Using Eq \@ref(eq:C-beta), we inferred the contribution of landscape variables to the estimated slope of thermal sensitivity. Principal components of landscape variables explained 98% of variance in $bm{\phi}$, the measures of the steepest slope in Eq. \@ref(eq:MohseniModel).

### Landscape Effects on Thermal Sensitivity
Principal components of landscape characteristics varied in their influence on stream thermal sensitivity. The $\theta$ value for PC3, characterized by latitude, longitude, baseflow index, precipitation, minimum air temperature, and winter stream velocity (Table \@ref(tab:PCs-table)), was significantly negative with a posterior mean value of `r round(thetas.table[3, "mean"], 2)` (95% HPDI: `r round(thetas.table[3,4], 2)` to `r round(thetas.table[3,5], 2)`). The $\theta$ value for PC5, characterized by soils, slope, landcover, and water table depth, was significantly positive with a posterior mean value of `r round(thetas.table[5, "mean"], 2)` (95% HPDI: `r round(thetas.table[5,4], 2)` to `r round(thetas.table[5,5], 2)`). The posterior mean $\theta$ values for PC1 and PC4 were positive and for PC2 were negative, but 95% HPDIs overlapped with 0 (Fig. \@ref(fig:theta-posteriors)).

(ref:theta-posteriors-cap) Full posterior distributions for Eq. \@ref(eq:PCALinear) $\bm{\theta}$ values. $\bm{\theta)$ represent the contributions of principal components 1-5 to $\bm{\phi}$, the measure of maximum slope of the nonlinear equation (Eq. \@ref(eq:MohseniModel)).

```{r theta-posteriors, fig.cap="(ref:theta-posteriors-cap)"}
theta_posteriors.plot
```

### Predictions of Thermal Sensitivity
We used posterior parameter estimates from Model \@ref(eq:MohseniModel) to predict thermal sensitivity at unsampled brook trout habitat. Predicted $bm{\beta}$ ranged from __ to __ at these sites. 