---
title: ''
output: bookdown::pdf_document2
---
## Principal Components Analysis
The first principal component was dominated by estimates of monthly and annual stream flow (Table \@ref(tab:PCs-table)). The second principal component was made up of metrics of spring and summer stream velocity. The third principal component included winter stream velocity and elevation, but also incorporated estimated temperature maximums within the catchment. The fourth principal component included groundwater (baseflow and water table depth), precipitation estimates, and minimum temperatures. The fifth and final principal component was dominated by measures of soil moisture, urban and deciduous landcover, and local colluviated (unconsolidated) sediment. The first five principal components explained `r round(pca_summary.table["Cumulative R2", "PC5"], 3) * 100`% of the variance in predictors (Table \@ref(tab:PCs-table)).

(ref:PCs-table-cap) Top five principal components (PCs) by variance explained (R$^2$). The top ten contributing variables for each principal component are included. "Q" variables refer to stream flow metrics during specified periods of the year (numbers = months and MA = mean annual), and "V" variables refer to stream velocity. Further variable definitions are available from the [EPA StreamCat](https://www.epa.gov/national-aquatic-resource-surveys/streamcat-metrics-and-definitions) database.

```{r PCs-table}
kbl(top.loadings.table,
    caption = "(ref:PCs-table-cap)") %>% 
  #column_spec(6, width = "3cm") %>% 
  kable_styling(full_width = T,
                latex_options = "HOLD_position") %>% 
  kable_classic()
```

## Hierarchical Models
### Model Comparison
All parameters converged at $\hat{r}$} values of 1.1 or less. Models of weekly maximum temperature offered a superior fit to daily maximum temperature, and the nonlinear models outperformed the linear models. For the linear models, DIC improved from 841,653 to 123,409 and RMSE improved from __ to 3.76 (95% HPDI: 3.73 to 3.79) going from the daily to weekly time scale. For the nonlinear models, DIC improved from 855,368 to 121,355 and RMSE improved from __ to 3.58 (95% HPDI: 3.56 to 3.62) going from daily to weekly time scales. Posterior predictive checks suggest little evidence of lack of fit between model estimates and data. Mean Bayesian p-values for mean and standard deviation for the linear model at the daily time scale were ___ and __ . For the linear model at the weekly time scale they were `r round(Weekly_Max_LM_PPC_summ.table["Mean", 2], 2)` and `r round(Weekly_Max_LM_PPC_summ.table["Mean", 3], 2)`. Mean Bayesian p-values for the nonlinear model at the daily scale were __ and __ and `r round(Weekly_Max_Logistic_PPC_summ.table["Mean", 2], 2)` and `r round(Weekly_Max_Logistic_PPC_summ.table["Mean", 3], 2)` for the nonlinear model at the weekly time scale.

### Thermal Sensitivity
Linear regression slopes were higher with temperatures summarized at the weekly time scale than the daily time scale (mean slope of `r round(mean(weekly_linear_slopes.table$mean), 2)` as compared to `r round(mean(daily_linear_slopes.table$mean), 2)`. Slopes ranged from `r round(min(daily_linear_slopes.table$mean), 2)` (95% HPDI = `r round(daily_linear_slopes.table[which.min(daily_linear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(daily_linear_slopes.table[which.min(daily_linear_slopes.table$mean), "95%_HPDU"], 2)`) to `r round(max(daily_linear_slopes.table$mean), 2)` (95% HPDI = `r round(daily_linear_slopes.table[which.max(daily_linear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(daily_linear_slopes.table[which.max(daily_linear_slopes.table$mean), "95%_HPDU"], 2)`) for temperatures at the daily time scale and from `r round(min(weekly_linear_slopes.table$mean), 2)` (95% HPDI = `r round(weekly_linear_slopes.table[which.min(weekly_linear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(weekly_linear_slopes.table[which.min(weekly_linear_slopes.table$mean), "95%_HPDU"], 2)`) to `r round(max(weekly_linear_slopes.table$mean), 2)` (95% HPDI = `r round(weekly_linear_slopes.table[which.max(weekly_linear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(weekly_linear_slopes.table[which.max(weekly_linear_slopes.table$mean), "95%_HPDU"], 2)`) for temperatures at the weekly time scale. Likewise, nonlinear regression maximum slopes were higher with temperatures summarized at the weekly time scale than the daily time scale (mean slope of `r round(mean(weekly_nonlinear_slopes.table$mean), 2)` as compared to `r round(mean(daily_nonlinear_slopes.table$mean), 2)`. Slopes ranged from `r round(min(daily_nonlinear_slopes.table$mean), 2)` (95% HPDI = `r round(daily_nonlinear_slopes.table[which.min(daily_nonlinear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(daily_nonlinear_slopes.table[which.min(daily_nonlinear_slopes.table$mean), "95%_HPDU"], 2)`) to `r round(max(daily_nonlinear_slopes.table$mean), 2)` (95% HPDI = `r round(daily_nonlinear_slopes.table[which.max(daily_nonlinear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(daily_nonlinear_slopes.table[which.max(daily_nonlinear_slopes.table$mean), "95%_HPDU"], 2)`) for temperatures at the daily time scale and from `r round(min(weekly_nonlinear_slopes.table$mean), 2)` (95% HPDI = `r round(weekly_nonlinear_slopes.table[which.min(weekly_nonlinear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(weekly_nonlinear_slopes.table[which.min(weekly_nonlinear_slopes.table$mean), "95%_HPDU"], 2)`) to `r round(max(weekly_nonlinear_slopes.table$mean), 2)` (95% HPDI = `r round(weekly_nonlinear_slopes.table[which.max(weekly_nonlinear_slopes.table$mean), "95%_HPDL"], 2)` to `r round(weekly_nonlinear_slopes.table[which.max(weekly_nonlinear_slopes.table$mean), "95%_HPDU"], 2)`) for temperatures at the weekly time scale. Nonlinear measures of maximum slope were highly correlated with linear slopes (daily = `r round(cor(daily_linear_slopes.table$mean, daily_nonlinear_slopes.table$mean, method = "pearson"), 2)`, weekly = `r round(cor(weekly_linear_slopes.table$mean, weekly_nonlinear_slopes.table$mean, method = "pearson"), 2)`; Pearson's). Slopes were heterogeneous in space (Fig. \@ref(fig:slopes-map)). There was no spatial structure in these slopes (Appendix \@ref(fig:logistic-weekly-betas-semivariogram-plot)).

```{r slopes-map, fig.cap="Air-water temperature slopes for each of 203 measurement sites. Slopes are $\beta$ values from the nonlear model of maximum weekly temperatures."}
betas_map.plot
```

Principal components of landscape variables explained 98% of variance in $bm{\phi}$, the measures of the steepest slope in the logistic equations.

There was considerable spatial structure in thermal sensitivity (*link to semivariogram of betas*)

### Landscape Effects on Thermal Sensitivity
PC1, characterized by estimates of streamflow, had a significantly negative effect on thermal sensitivity; while PC2, characterized by estimates of stream velocity, had a significantly positive effect on thermal sensitivity. PC4, characterized by elevation, precipitation estimates, soil wetness and organic matter, and stream order, had a slightly lesser but still positive effect on thermal sensitivity. Principal components three and five did not significantly effect thermal sensitivity.