---
title: ''
output: bookdown::pdf_document2
---
## Principal Components Analysis
The first principal component was dominated by estimates of monthly and annual stream flow (Table \@ref(tab:PCs-table)). The second principal component was made up of metrics of spring and summer stream velocity. The third principal component included winter stream velocity and elevation, but also incorporated estimated temperature maximums within the catchment. The fourth principal component included groundwater (baseflow and water table depth), precipitation estimates, and minimum temperatures. The fifth and final principal component was dominated by measures of soil moisture, urban and deciduous landcover, and local colluviated (unconsolidated) sediment. The first five principal components explained `r round(pca_summary.table["Cumulative R2", "PC5"], 3) * 100`% of the variance in predictors (Table \@ref(tab:PCs-table)).

(ref:PCs-table-cap) Top five principal components (PCs) by variance explained (R$^2$). The top ten contributing variables for each principal component are included. "Q" variables refer to stream flow metrics during specified periods of the year (numbers = months and MA = mean annual), and "V" variables refer to stream velocity. Further variable definitions are available from the [NHDPlus User Guide](https://pubs.er.usgs.gov/publication/ofr20191096) and [EPA StreamCat](https://www.epa.gov/national-aquatic-resource-surveys/streamcat-metrics-and-definitions) database.

```{r PCs-table}
kbl(top.loadings.table,
    caption = "(ref:PCs-table-cap)",
    row.names = T) %>% 
  kable_styling(full_width = T,
                latex_options = "HOLD_position") %>% 
  kable_classic()
```

## Logistic Model

All parameters converged. Posterior predictive checks suggested little evidence of lack of fit between model estimates and data. Mean Bayesian p-values for mean and standard deviation were `r round(Weekly_Mean_Logistic_PPC_summ.table["Mean", 1], 2)` and `r round(Weekly_Mean_Logistic_PPC_summ.table["Mean", 2], 2)`. Linear and nonlinear models performed quite similarly, and the three metrics of model fit did not consistently favor one model over the other. The nonlinear had a slightly higher mean R$^2$ than the linear model (`r round(model_fits.table["Weekly_LM", "R2"], 2)` vs. `r round(model_fits.table["Weekly_Logistic", "R2"], 2)`), but the linear model had lower RMSE (`r round(model_fits.table["Weekly_LM", "RMSE"], 2)` vs. `r round(model_fits.table["Weekly_Logistic", "RMSE"], 2)`, Appendix ). Posterior predictive checks were nearly identical between the two models.

### Thermal Sensitivity
Logistic regression slopes varied from `r round(min(weekly_nonlinear_slopes.table$mean), 2)` (95% HPDI: to ) to `r round(max(weekly_nonlinear_slopes.table$mean), 2)` (95% HPDI: to ), with an average slope of `r round(mean(weekly_nonlinear_slopes.table$mean), 2)` (Fig. \@ref(fig:logistic-fits-plot)). These slopes were highly correlated with slopes from the linear regression (`r round(cor(weekly_linear_slopes.table$mean, weekly_nonlinear_slopes.table$mean, method = "pearson"), 2)`, Pearson's). Slopes were heterogeneous in space (Fig. \@ref(fig:slopes-map)), and several sites had particularly low and high slopes, indicating certain habitats with thermal stability or thermal elasticity. A latitudinal gradient was apparent, with lower slopes generally present at  southerly sites. There was also evidence of spatial autocorrelation in thermal sensitivity (Appendix \@ref(fig:logistic-weekly-betas-semivariogram-plot)). $\bm{\beta}$ was correlated with the range of stream temperatures experienced at a site (Appendix \@ref(fig:nonlinear-betas-corr-plot)), corroborating the idea that small $\bm{\beta}$ equates to thermal stability.

(ref:logistic-fits-plot-cap) Logistic regression fits for a) Ewin Run near Laurel Branch, WV, USA and b) Blackwater River near Cortland, WV, USA. Black dots represent paired weekly average temperatures and red lines represent logistic regressions.
```{r logistic-fits-plot, fig.cap="(ref:logistic-fits-plot-cap)"}
plot_grid(lowest_beta.plot,
          highest_beta.plot,
          labels = c("a)", "b)"),
          label_size = 11,
          nrow = 1)
```

```{r slopes-map, fig.cap="Air-water temperature slopes for each of 203 measurement sites. Slopes are $\bm{\beta}$ values from the nonlear model of maximum weekly temperatures."}
betas_map.plot
```

Correlation analysis demonstrated an association between thermal sensitivity (as measured by the nonlinear regression using weekly temperatures) and local landscape. Thermal sensitivity was most closely correlated with segment slope, baseflow index (an estimate of groundwater influence), winter flow, and stream segment location and drainage area (Table \@ref(tab:weekly-logistic-betas-corr-table)). Using Eq. \@ref(eq:C-phi), we inferred the contribution of landscape variables to the estimated slope of thermal sensitivity. Principal components of landscape variables explained 99% of variance in $\bm{\phi}$, the measures of the steepest slope in Eq. \@ref(eq:MohseniModel).

### Landscape Effects on Thermal Sensitivity
Principal components of landscape characteristics varied in their influence on stream thermal sensitivity. The $\theta$ value for PC3, characterized by latitude, longitude, baseflow index, precipitation, minimum air temperature, and winter stream velocity (Table \@ref(tab:PCs-table)), was significantly negative with a posterior mean value of `r round(nonlinear_thetas.table[3, "mean"], 2)` (95% HPDI: `r round(nonlinear_thetas.table[3,4], 2)` to `r round(nonlinear_thetas.table[3,5], 2)`). The $\theta$ value for PC5, characterized by soils, slope, landcover, and water table depth, was significantly positive with a posterior mean value of `r round(nonlinear_thetas.table[5, "mean"], 2)` (95% HPDI: `r round(nonlinear_thetas.table[5,4], 2)` to `r round(nonlinear_thetas.table[5,5], 2)`). The posterior mean $\theta$ values for PC1 and PC4 were positive and for PC2 were negative, but 95% HPDIs overlapped with 0 (Fig. \@ref(fig:nonlinear-theta-posteriors-plot)).

(ref:nonlinear-theta-posteriors-plot-cap) Full posterior distributions for Eq. \@ref(eq:PCALinear) $\bm{\theta}$ values. $\bm{\theta}$ represent the contributions of principal components 1-5 to $\bm{\phi}$, the measure of maximum slope of the nonlinear equation (Eq. \@ref(eq:MohseniModel)).

```{r nonlinear-theta-posteriors-plot, fig.cap="(ref:nonlinear-theta-posteriors-plot-cap)"}
nonlinear_theta_posteriors.plot
```

### Predictions of Thermal Sensitivity
We predicted thermal sensitivity at unsampled brook trout habitat throughout the study region using Eq. \@ref(eq:MohseniModel). Predicted $\bm{\beta}$ ranged from `r round(min(trout_site_nonlinear_betas.table$pstr_mean_nonlinear_beta), 2)` (95% CI: `r round(trout_site_nonlinear_betas.table[which.min(trout_site_nonlinear_betas.table$pstr_mean_nonlinear_beta), 3], 2)` to `r round(trout_site_nonlinear_betas.table[which.min(trout_site_nonlinear_betas.table$pstr_mean_nonlinear_beta), 4], 2)`) to `r round(max(trout_site_nonlinear_betas.table$pstr_mean_nonlinear_beta), 2)` (95% CI: `r round(trout_site_nonlinear_betas.table[which.max(trout_site_nonlinear_betas.table$pstr_mean_nonlinear_beta), 3], 2)` to `r round(trout_site_nonlinear_betas.table[which.max(trout_site_nonlinear_betas.table$pstr_mean_nonlinear_beta), 4], 2)`) at these sites, and varied greatly across the study region (Fig. \@ref(fig:beta-predictions-plot)). Among others, the Monongahela National Forest and the Great Smoky Mountains were predicted to have particularly stable stream temperatures. A latitudinal gradient in slopes was also apparent here, further demonstrating the influence of latitude on thermal sensitivity. Our predictions highlighted several sites likely to have exceptionally stable or elastic thermal patterns. Defining preferred thermal habitat as the lowest 25th percentile of predicted thermal stability values, we found that 63% of preferred thermal habitat lies within protected areas.

(ref:beta-predictions-plot) Predicted stream thermal stability at 8,660 sites of brook trout habitat in the southeastern USA. Thermal stability was predicted using posterior estimates from Eqs. \@ref(eq:PCALinear) and \@ref(eq:MohseniModel), as well as spatially interpolated minimum and maximum stream temperatures. 

```{r beta-predictions-plot, fig.cap="(ref:beta-predictions-plot)"}
nonlinear_betas_pred_map.plot
```